---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(bmarketing)
library(rpart)
library(rpart.plot)
```
# bmarketing

<!-- badges: start -->
<!-- badges: end -->

The goal of bmarketing is to provide functions useful for data cleansing, modelling and reporting tasks.

## Installation

You can install the released version of bmarketing from [Github](https://github.com/BalintKomjati/bmarketing) with: 

```{r}
devtools::install_github("BalintKomjati/bmarketing")
library(bmarketing)
```

## Example

This is a basic workflow for package usage is the following:

1) Import the package

```{r}
library(bmarketing)
```

2) Import the data you want to analyse. Like

```{r}
bmarketing <- read.csv2("inst/bmarketing.csv",dec = ".")
```

3) Do some data cleansing with function clean()

```{r}
bmarketing <- clean(x = bmarketing, t = "y")
```

4) Fit a Decision Tree, plot the results, give predictions:

```{r}
dt_model<- rpart(y ~ ., data = bmarketing)
rpart.plot(dt_model)

predictions <- predict(dt_model, bmarketing, type = "class")
```

5) Finally, you can create a report for model performance:
```{r}
calcPerformance(y = bmarketing$y, y_pred = predictions)
```

