---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## Overview

This package offers a series of functions that will clean, transform and build a decision tree model for your input dataset. The functions are split in different R scripts inside the R folder and should be executed as explained below. 

## Function Description

clean_data : This function will check if the target variable contains missing calues and returns an error. It also gives warnings if other variables contain NAs and removes thoe columns that have more than 50% NAs. 

transform_data : Data transformation step transforms the numeric variables using log and transforms factors into numeric variables (and vice versa).

model_data : This function builds a decision tree for the provided dataset. 

model_plot : Plots the decision tree created in the precious step.

model_predict: Returns the predicted classes from the decision tree.

model_performance : This functions calculated the accuracy of the model. 

## Usage

Here is how to use the package

```{r}
library(bmarketing)
df <- import_data_from_csv("~/CloudStation/Projekte/r_projects/bmarketing2.csv")
##clean_data(df, target_var = "Y")

df[is.na(df$Y), "Y"] <- 0
df <- clean_data(df, target_var = "Y")

df <- transform_data(df, c("AGE", "DURATION"))

target_var <- "Y"
m <- model_data(df, target_var)

model_plot(m)

target <- df[, target_var][[1]]
predictions <- model_predict(m, df)


model_performance(target, predictions)
```



