---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

[![Travis Build Status](https://travis-ci.org/Quantargo/bmarketing.svg?branch=master)](https://travis-ci.org/Quantargo/bmarketing)
[![Coverage Status](https://img.shields.io/codecov/c/github/Quantargo/bmarketing/master.svg)](https://codecov.io/github/Quantargo/bmarketing?branch=master)

## Overview

This package is dedicated to classification analysis using decision trees. Aside from decision tree model itself and prediction function it has got all necessary supporting tools - data cleaning, transformation function, plot of the results and calculation of accuracy of predictions and confusion matrix.

## Functionalities

The functionalities are as follows.

* Data Cleaning

```{r}
require("tree3")

data("bmarketing")
cleanedData <- clean(data = bmarketing,target_name = "y")
```

* Data Transforming
```{r}
cleanedData$cons.price.id <- transform(cleanedData,column = "cons.price.idx")
```

* Finding a Model
```{r}
treeModel <-  model(input_data = cleanedData,target_name="y")
```


* Getting the predictions
```{r}
predictionData <-  predictions(dt_model = treeModel,data = cleanedData)
```

* Assessing the model accuracy
```{r}
model_accuracy(real = cleanedData$y,pred = predictionData,chosenvar='yes')
```
